***De novo* clustering methods out-perform reference-based methods for assigning 16S rRNA gene sequences to operational taxonomic units**

### 2015-10-13 Schloss_Cluster_PeerJ_2015.Rmd
Add rules for rendering paper

***454 FLX-generated Roesch Canadian soil dataset***
After obtaining the 16S rRNA gene fragments from GenBank (accessions EF308591-EF361836), we followed the methods outlined by the He study by removing any sequence that contained an ambiguous base, was identified as being a chimera, and fell outside a defined sequence length. Although they reported observing a total of 50,542 sequences that were represented by 13,293 unique sequences, we obtained a total of `r length(scan("data/he/canada_soil.good.unique.pick.redundant.fasta", what="", sep="\n", quiet=T))/2` sequences that were represented by `r length(scan("data/he/canada_soil.good.unique.pick.fasta", what="", sep="\n", quiet=T))/2` unique sequences. Similar to the He study, we randomly sampled, without replacement, 20, 40, 60, and 80% of the sequences from the full data set. The random sampling was repeated 30 times. The order of the sequences in the full dataset was randomly permuted without replacement to generate an additional 30 datasets. To perform the hierarchical clustering methods and to generate a distance matrix we followed their approach of the He study by calculating distances based on pairwise global alignments using the `pairwise.dist` command in mothur using the default Needleman-Wunsch alignment method and parameters. It should be noted that this method has been strongly discouraged (REFS). Execution of the hierarchical clustering methods was performed as described in the original He study using mothur (v.1.37) and using the QIIME (v.1.9.1) parameter profiles provided in the supplementary material from the He study for the greedy and reference-based clustering methods.

>>>>

***454 FLX-generated Roesch Canadian soil dataset***
After obtaining the 16S rRNA gene fragments from GenBank (accessions EF308591-EF361836), we followed the methods outlined by the He study by removing any sequence that contained an ambiguous base, was identified as being a chimera, and fell outside a defined sequence length. Although they reported observing a total of 50,542 sequences that were represented by 13,293 unique sequences, we obtained a total of `r length(scan(file="data/he/canada_soil.good.unique.pick.redundant.fasta", what="", sep="\n", quiet=T))/2` sequences that were represented by `r length(scan(file="data/he/canada_soil.good.unique.pick.fasta", what="", sep="\n", quiet=T))/2` unique sequences. Similar to the He study, we randomly sampled, without replacement, 20, 40, 60, and 80% of the sequences from the full data set. The random sampling was repeated 30 times. The order of the sequences in the full dataset was randomly permuted without replacement to generate an additional 30 datasets. To perform the hierarchical clustering methods and to generate a distance matrix we followed their approach of the He study by calculating distances based on pairwise global alignments using the `pairwise.dist` command in mothur using the default Needleman-Wunsch alignment method and parameters. It should be noted that this method has been strongly discouraged (REFS). Execution of the hierarchical clustering methods was performed as described in the original He study using mothur (v.1.37) and using the QIIME (v.1.9.1) parameter profiles provided in the supplementary material from the He study for the greedy and reference-based clustering methods.
